### 2016-03-14 paper/result_layered_depthmap.tex
results

From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself. Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here. To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.

As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings. For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.

>>>>

We plot the energy minimization process in figure \ref{fig:layered_depthmap_convergence}. From the plot, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state. The reason is binary fusion of solution proposals (either from others or self) is too limited to contain a lower energy state due to the complexity of the problem itself. Only when multi-way fusion which explores much larger solution space is used (in FS-SS and FS), it becomes possible for the energy to further decrease. This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here. Note that FS also utilize multi-way fusion for solution sharing so that it performs better than FS-SS which has no solution sharing.

To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy minimization process in figure \ref{fig:layered_depthmap_by_alpha}. We can see that as the number of ways to fuse becomes larger, each fusion step takes longer time, but the chance of finding a lower energy state increases.

As shown in section \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different problem settings.
